%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% How to use writeLaTeX:
%
% You edit the source code here on the left, and the preview on the
% right shows you the result within a few seconds.
%
% Bookmark this page and share the URL with your co-authors. They can
% edit at the same time!
%
% You can upload figures, bibliographies, custom classes and
% styles using the files menu.
%
% Modifyied by Prof. MSc. Daniel Menin Tortelli
% Computer Science - URICER - Brazil
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article}

\usepackage{article-config/sbc-template}

\usepackage{graphicx,url}

\usepackage[brazilian]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{graphicx,url}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{textcomp}
\usepackage{url}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{soul}
\usepackage{verbatim}
\usepackage[table,xcdraw]{xcolor}
\usepackage[shortlabels]{enumitem}
\usepackage{scalefnt}
\usepackage{comment}
\usepackage{lscape}
\usepackage{fancyhdr}
\usepackage{article-config/pages-style}
\usepackage[super]{nth}
\usepackage[table]{xcolor}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usetikzlibrary{positioning,calc}
\usepackage{float}


\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\sloppy

\input{article-config/event-info}

\title{ValorizeAI: Documentação e Validação de uma Arquitetura Serverless Elasticamente Gerenciada \\
\medskip
\small{
    \textit{Title: ValorizeAI: Documenting and Validating a Managed Serverless Architecture}
}
}

\author{Felipe Tomkiel Malacarne, Prof. Me. Marcos André Lucas}

\address{
    Universidade Regional Integrada do Alto Uruguai e das Missões \\
    Departamento de Engenharias e Ciência da Computação\\
  Caixa Postal 743 -- 99.709-910 -- Erechim -- RS -- Brasil
\email{101090@uricer.edu.br, mlucas@uricer.edu.br}
}

\begin{document}

\maketitle

\thispagestyle{plain}
\pagestyle{plain2}


\begin{resumo}
Plataformas financeiras modernas exigem arquiteturas elásticas capazes de absorver picos de carga transacional sem comprometer consistência forte ou observabilidade. Este trabalho documenta e valida o ValorizeAI, uma aplicação real de categorização automática construída sobre Google Cloud Run, Cloud SQL, Redis (Memorystore), Cloud Tasks e WebSockets. A pesquisa adota uma abordagem aplicada inspirada em SRE: os SLOs (latência P95 $\leq$ 300~ms, erro $<$ 0,5\%, disponibilidade $\geq$ 99{,}5\%) são definidos previamente, a infraestrutura é provisionada como código e os testes k6 abrangem cenários de leitura intensiva, leitura/escrita e o pipeline assíncrono. O cenário de leitura sustentou 1{,}000 usuários virtuais (média de 470 req/s, pico de $\approx$970 req/s) com P95 de 158~ms; o cenário misto manteve 226 req/s com 650 VUs e violou o SLO a partir de $\approx$539 VUs, elevando o P95 para 658~ms e o p99 para 2,67~s ao saturar a cota de 10 instâncias do Cloud Run. O pipeline assíncrono processou 51,58 mil tarefas em 10 minutos (86 tarefas/s) sem perdas. Conclui-se que a arquitetura atende confortavelmente workloads intensivos em leitura e que o suporte a escritas altamente concorrentes requer aumento de instâncias HTTP ou otimizações específicas no caminho de escrita.
\end{resumo}

\palavraschave{Computação Serverless, Cloud Run, Plataformas Financeiras, Testes de Carga, Observabilidade.}

\begin{abstract}
Modern financial workloads demand elastic architectures capable of sustaining variable traffic while preserving strong consistency and system observability. This paper documents and validates ValorizeAI, a real-world automated categorization platform built on Cloud Run, Cloud SQL, Redis, Cloud Tasks, and WebSockets. The study adopts an applied SRE-inspired methodology: SLOs (P95 latency $\leq$ 300~ms, error rate $<$ 0.5\%, availability $\geq$ 99.5\%) are defined beforehand, infrastructure is provisioned as code, and k6 executes read-only, mixed read/write, and asynchronous-pipeline load scenarios. The read scenario supported 1,000 virtual users (mean 470 req/s, peak $\approx$970 req/s) with P95 = 158~ms and zero failures; the mixed scenario sustained 226 req/s at 650 VUs and violated the SLO around $\approx$539 VUs, reaching P95 = 658~ms and p99 = 2.67~s once the 10-instance Cloud Run quota was saturated. The asynchronous pipeline processed 51.58k Cloud Tasks in 10 minutes (86 tasks/s) with no loss or duplication. The results show that the architecture comfortably supports read-heavy traffic, while higher write concurrency requires additional horizontal scaling or optimizations in the write path.
\end{abstract}

\keywords{Serverless Computing, Cloud Run, Financial Platforms, Performance Testing, Observability.}

\input{sections/1-introduction}
\input{sections/2-related-works}
\input{sections/3-theoretical-framework}
\input{sections/4-metodology}
\input{sections/5-implementation}
\input{sections/6-results}
\input{sections/7-conclusion}
\newpage

% \nocite{BCB_Economia_Bancaria_2024,Febraban_Tecnologia_2024,Febraban_Transacoes_2025}

\bibliographystyle{article-config/sbc}
\bibliography{references/references}

\end{document}
